OCMu64: a solver for One-sided Crossing Minimization

### 2024-06-20 tex/description.tex
Further changes to the description

% todo from here
\begin{lemma}[Practically fixed pair]\label{pfp}
  Suppose $r(u,v)\leq 0$.
  A \emph{blocking} set $X\subseteq B-\{u,v\}$ is a set such that $c(v,X,u)$ is
  stricly better than both $c(u,v,X)$ and $c(X,u,v)$.
  If there is no blocking set, then $u\be v$.
\end{lemma}

In practice, such a set $X$ can be found, if one exists, using knapsack: for
each $x\in B-\{u,v\}$, add a point $P_x = (r(v, x), r(x, u))$, and search for a
subset summing to ${\leq{}(r(u, v), r(u, v))}$.

Note that we do not require $(v, X, u)$ to be a true local minimum, since we do
not consider interactions between vertices in $X$, as that would make finding
such sets much harder.

>>>>

\begin{lemma}[Practically fixed pair]\label{pfp}
  Suppose $r(u,v)\leq 0$.
    A \emph{blocking set} $X\subseteq B-\{u,v\}$ is a set such that $c(v,X,u) < \min(c(v, u,
    X), (X, v, u))$.  If there is no blocking set for $(u, v)$, then $u\b v$.
\end{lemma}

In practice, such a set $X$ can be found, if one exists, using a knapsack-like algorithm: for
each $x\in B-\{u,v\}$, add a point $P_x = (r(v, x), r(x, u))$, and search for a subset summing
to ${\leq{}(r(u, v), r(u, v))}$.

Note that we do not require $(v, X, u)$ to be a true local minimum, since we do
not consider interactions between vertices in $X$, as that would make ruling out the
existence of such sets much harder.
